\section{Margin Models}
\label{sec:MarginModels}

\textbf{Margin Models} are models designed to calculate the margin of a component for margin-based reliability 
calculations.

The classes of models considered here are as follows:
\begin{itemize}
	\item PointSetMarginModel, i.e. model \xmlAttr{type} is \xmlString{PointSetMarginModel}
\end{itemize}

The specifications of these models must be defined within a RAVEN \xmlNode{ExternalModel}. This
XML node accepts the following attributes:
\begin{itemize}
	\item \xmlAttr{name}, \xmlDesc{required string attribute}, user-defined identifier of this model.
	\nb As with other objects, this identifier can be used to reference this specific entity from other
	input blocks in the XML.
	\item \xmlAttr{subType}, \xmlDesc{required string attribute}, defines which of the subtypes should
	be used. For margin models, the user must use \xmlString{SR2ML.MarginModel} as subtype.
\end{itemize}

In the margin \xmlNode{ExternalModel} input block, the following XML subnodes are required:
\begin{itemize}
	\item \xmlNode{variable}, \xmlDesc{string, required parameter}. Comma-separated list of variable
	names. Each variable name needs to match a variable used or defined in the matign model or variable
	coming from other RAVEN entities (i.e., Samplers, DataObjects, and Models).
	\item \xmlNode{MarginModel}, \xmlDesc{required parameter}. The node is used to define the maintenance
	model, and it contains the following required XML attribute:
	\begin{itemize}
		\item \xmlAttr{type}, \xmlDesc{required string attribute}, user-defined identifier of the margin model.
	\end{itemize}
\end{itemize}

In addition, if the user wants to use the \textbf{alias} system, the following XML block can be input:
\begin{itemize}
	\item \xmlNode{alias} \xmlDesc{string, optional field} specifies alias for
	any variable of interest in the input or output space for the ExternalModel.
	%
	These aliases can be used anywhere in the RAVEN input to refer to the ExternalModel
	variables.
	%
	In the body of this node, the user specifies the name of the variable that the ExternalModel is
	going to use (during its execution).
	%
	The actual alias, usable throughout the RAVEN input, is instead defined in the
	\xmlAttr{variable} attribute of this tag.
	\\The user can specify aliases for both the input and the output space. As a sanity check, RAVEN
	requires an additional required attribute \xmlAttr{type}. This attribute can be either ``input'' or ``output.''
	%
	\nb The user can specify as many aliases as needed.
	%
	\default{None}
\end{itemize}

\subsection{PointSetMarginModel Model}
For the PointSetMarginModel model, in the margin \xmlNode{MarginModel} input block, the following XML subnodes 
are required:
\begin{itemize}
	\item \xmlNode{failedDataFileID}, \xmlDesc{string, required parameter}. ID of the file containing the failure data
	      to be used as reference data
	\item \xmlNode{marginID}, \xmlDesc{required parameter}. ID of the variable where the margin needs to be stored
	\item \xmlNode{map}, \xmlDesc{required parameter}. This node is used to map actual measured data dimension and the 
	      failure data dimension. In here, the ID of the Raven variable representing a dimension of the actual data
	\begin{itemize}
		\item \xmlAttr{var}, \xmlDesc{required string attribute}, the ID of the corresponding dimension in the failure data.
	\end{itemize}
\end{itemize}

Example XML:
\begin{lstlisting}[style=XML]
    <ExternalModel name="PointSetMargin" subType="SR2ML.MarginModel">
      <variables>actualTime,actualTemp,marginPS1</variables>
      <MarginModel type="PointSetMarginModel">
        <failedDataFileID>failureData.csv</failedDataFileID>
        <marginID>marginPS1</marginID>
        <map var='time'>actualTime</map>
        <map var='avgT'>actualTemp</map>
      </MarginModel>
    </ExternalModel>
\end{lstlisting}